### 2020-06-02 writeup/intro.tex
abstract

\begin{abstract}
When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
In this work, we address this question by studying
% the performance of predicting a particular task given multiple tasks.
a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
First, for the setting of high-dimensional linear regression, we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
We provide an analysis of the tradeoff and extend the result to transfer learning.
We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
Second, we identify three components including task similarity, data size and covariate shift to explain negative transfer in multi-task learning rigorously.
Finally, we show practical implications of our theory for detecting and mitigating negative transfer.
We propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
We validate our theory and our proposed method on image and text classification tasks.
\end{abstract}

>>>>

\begin{abstract}
%When does multi-task learning provide positive (or negative) information transfer, compared to single-task learning?
	Multi-task learning is a powerful approach to solve complex tasks in many applications such as image and text classification.
	Yet, there is little rigorous understanding of when multi-task learning performs well, even compared to single-task learning.
	In this work, we study this question formally by considering three components including \textit{task similarity}, \textit{sample size} and \textit{covariate shift} in the setting of high-dimensional linear regression.
% the performance of predicting a particular task given multiple tasks.
%a multi-task learning architecture that uses a shared layer for all tasks and a separate output layer for each task.
	First, we show that whether multi-task learning performs better than single-task learning is determined by the bias-variance tradeoff of multi-task estimators.
	We analyze the bias-variance tradeoff by developing technical tools using random matrix theory.
	%we show that the type of transfer is determined by the bias-variance tradeoff of multi-task learning estimators.
	%We develop a technical tool to analyze the.
%	We develop a technical tool on the inverse of the sum of two random matrices that naturally arises from the analysis.
	Second, we apply our tools to show that the performance of multi-task learning is negatively affected as a result of: (a) decreased task similarity;
	(b) increased source sample size; (c) covariate shift under increased source sample sizes.
	Finally, we validate the three components of our theory on image and text classification tasks.
	Inspired by our theory, we propose an incremental training scheduler for improving the efficiency of multi-task training for predicting a particular task.
%	We validate our theory and our proposed method .
\end{abstract}
